Hello, reader and possible new employee at the prestiguous TicText organization. This document exists to help familiarize you with this project and its history. We will first introduce what TicText is, our motiviation, and even the biggest risks/challenges we face. Then, you will learn the software development processes we follow. Next, you will read a brief overview of the project's requirements and specifications before diving into the current architecture and design. Finally, we hope a brief outline of future plans will help you find what you want to work on.

\begin{flushright}
Let's get started, Tic Tok!
\end{flushright}

\subsection{Prerequisites}
\begin{itemize}
	\item Xcode 6, preferably the latest version
	\item iOS 7
\end{itemize}

\subsection{Setting up your Xcode project}
\begin{enumerate}
	\item After downloading the latest copy of the repository, install all project dependencies from CocoaPods by running,
		\begin{verbatim}
		cd TicText-iOS
		pod install
		\end{verbatim}
	\item Open the Xcode workspace at \verb|TicText-iOS/TicText.xcworkspace|.
	\item Set up a, or ask permissions to our development, TicText app on Parse.
	\item Copy the environment's application id and client key into \verb|AppDelegate.m|:
		\begin{verbatim}
		[Parse setApplicationId:@"APPLICATION_ID" clientKey:@"CLIENT_KEY"];
		\end{verbatim}
	\item Finally, select the \verb|TicText| target and go to \verb|Build Phases|. Under \verb|Upload Symbol Files|, update line 3 to point to your Cloud Code folder, if any. If you're not using Cloud Code, feel free to remove the \verb|Upload Symbol Files| section.
\end{enumerate}

\subsection{Configuring TicText's Facebook integration}
\begin{enumerate}
	\item Set up a, or ask permission to our development, Facebook app at \url{http://developers.facebook.com/apps}.
	\item Set up a URL scheme for \verb|fbFACEBOOK_APP_ID|, where \verb|FACEBOOK_APP_ID| is your Facebook app's id.
	\item Add your Facebook app id to \verb|Info.plist| in the \verb|FacebookAppID| key.
\end{enumerate}

\subsection{Cloud Code}
Add your Parse app id and master key to \verb|TicText-iOS/CloudCode/config/global.json|, then type \verb|parse deploy| from the command line at \verb|TicText-cloud|. See the \href{https://parse.com/docs/cloud_code_guide#clt}{Cloud Code Guide} for more information about the \verb|parse| CLI.